9-distance-posthoc-analysis

### 2023-12-07 src/scripts/distance/9-distance-posthoc-analysis.Rmd
updated methods, results, and discussion of article based on j and a suggestions. still waiting for distance CV to finish

# Detectability Estimates
```{r detectability}
# Set constants based off predictions here and in the cue rate output
bith_cr <- c(0.28, 0.16, 0.48)
bith_edr <- c(73.1, 40.4, 135.0)
kiwa_cr <- c(0.29, 0.18, 0.48)
kiwa_edr <- c(75, 46.6, 124.8)
t = 5
r = 100

>>>>

# Detectability Estimates
```{r detectability}
# Set constants based off predictions here and in the cue rate output
bith_cr <- c(0.28, 0.16, 0.48)
bith_edr <- c(73.6, 40.5, 134.4)
kiwa_cr <- c(0.29, 0.18, 0.48)
kiwa_edr <- c(75.3, 45.9, 125.6)
t = 5
r = 100
